Machines are Among Us

### 2020-12-02 paper/main.tex
added part to results and started appendix
more additions, just pushing so i can take a break

At the end of voting, we calculate a ``crew score''. This score is simply the
maximum vote-off score that any imposter recieved, where votes
are averaged across all agents. Clearly, the imposters would like to minimize the
votes on themselves, so their loss function for training purposes is
simply the crew score. Inversely, the crew's loss function is the negation of
the crew score. This takes the form of a zero-sum game with similar application
as in generative adversarial networks.
\subsection{Training Scheme}
There were multiple decisions we had to make when attempting to train the models.
Imposter/Crew two different models, multitude of different hyperparameters and
sizes of inputs/outputs.
\subsection{Challenges}
The main challenge in building and running the model
came mainly in the form of training time, gradient overlap, 
and hyperparameter search. As discussed previously, to help speed up training time
and reduce gradient overlap between multiple different models training over the
same dataset, we had to only train either one imposter or crew, and keep the rest constant.
This limits the quick adaptivity, and may lead to the models attempting to train
against the constant tcooperative models ratrher than against the adversarial model.

@@

Another important challenge to recognize is the extreme "black box" architecture
of the model. With our current model iteration, we have no current approach to visualizing
exactly what the model is doing, especially with communication. Therefore there are
assumptions and estimations when creating conclusions about the model.
\subsection{Situation Hyperparameters}
To list the variable hyperparameters and input and outputs sizes for the player model,
overall, we have batch size, number of epochs, epoch length, the global LSTM hidden layer size, 
and the amount of players and imposters. For the perception phase, there is the
chance a player will view another player, the chance a sabotage occurs, and the number of $N$ events.  
The communication stage has variables the message size $M$ and the number of communication rounds
$R$.
\begin{figure*}
   \begin{center}
      \includegraphics[width=0.8 \textwidth]{img/grid_search.png}
   \end{center}
      \caption{A grid search heat map over the size parameters M (message vector) 
      and Rounds (the number of communications) displaying the ending Crew score after 6 epochs.
      }
   \label{fig:model}
\end{figure*}
\section{Results}
% talk about our goal for a qualitatively "good" communication
% session.
\subsection{Oscillating Scores}
% talk about problems we saw frequently. show examples of "good" runs
% and bad runs

% grid search results.
\subsection{Model Evolution}
% are the agents "improving" or just changing minorly to trick each other
\subsection{Interpreting Communcation Vectors}
\subsection{Future Directions}
This approach is just a start into understanding how neural networks
communicate with one another. Although assumptions can be made,
understanding the actual information being transferred between each model is
a dark area. Innovative techniques must be found to analyze this information flow 
in order to fully comprehend the strategy within the game.

@@

Finally, similar work in adversarial networks could potentially give rise to
more techniques utilizing them. Generative adversarial networks are at the forefront of adversarial techniques, but possibly
large multi-agent adervasarial communication networks could give heed to more good results.
{\small
\bibliographystyle{ieee_fullname}
\bibliography{egbib}
}

\end{document}

>>>>

At the end of voting, we calculate a ``crew score''. This score is simply the
maximum vote-off score that any imposter recieved, where votes
are averaged across all agents. Clearly, the imposters would like to minimize the
votes on themselves, so their loss function for training purposes is
simply the crew score. Inversely, the crew's loss function is the negation of
the crew score. This takes the form of a zero-sum game with similar application
as in generative adversarial networks.
\subsection{Training Scheme}
There were multiple decisions we had to make when attempting to train the models.
The two opposing models were trained
Imposter/Crew two different models, multitude of different hyperparameters and
sizes of inputs/outputs.
\subsection{Challenges}
The main challenge in building and running the model
came mainly in the form of training time, gradient overlap, 
and hyperparameter search. As discussed previously, to help speed up training time
and reduce gradient overlap between multiple different models training over the
same dataset, we had to only train either one imposter or crew, and keep the rest constant.
This limits the quick adaptivity, and may lead to the models attempting to train
against the constant tcooperative models ratrher than against the adversarial model.

@@

Another important challenge to recognize is the extreme "black box" architecture
of the model. With our current model iteration, we have no current approach to visualizing
exactly what the model is doing, especially with communication. Therefore there are
assumptions and estimations when creating conclusions about the model.
\subsection{Situation Hyperparameters}
To list the variable hyperparameters and input and outputs sizes for the player model,
overall, we have batch size, number of epochs, epoch length, the global LSTM hidden layer size, 
and the amount of players and imposters. For the perception phase, there is the
chance a player will view another player, the chance a sabotage occurs, and the number of $N$ events.  
The communication stage has variables the message size $M$ and the number of communication rounds
$R$.
\begin{figure*}
   \begin{center}
      \includegraphics[width=0.8 \textwidth]{img/grid_search.png}
   \end{center}
      \caption{A grid search heat map over the size parameters M (message vector) 
      and Rounds (the number of communications) displaying the ending Crew score after 6 epochs.
      }
   \label{fig:model}
\end{figure*}
\section{Results}
% talk about our goal for a qualitatively "good" communication
% session.
Due to the unprecedented architecture, we decided our overall goals
were to find the balance between imposter and crew
score, locate trends within the variable changes, and attempt to 
understand how the models communicate, to a degree. We conducted many
training sessions over multiple different combinations of variables.

A typical training session started with the first two initial epochs,
as discussed previously

Through our search, we found a trend to three different types of results:
an imposter 'win', a crew 'win', and a convergence.
An imposter win happens under certain circumstances where the crew are unable
to employ a better strategy than the crew's equally voting all other candidates.
A crew win occurs with the opposite---the crew can determine exactly who the imposters
are, and crew vote for one imposter. A convergence happens to place itself in the middle,
for what we assume to be a fair, balanced game between the two opposing parties.

Due to resource constraints, we were not able to get as much 
data as we had hoped for.
This lead to a consistency issue, where the same variable combination would yield
different results because of certain randomness within training the models.
\subsection{Oscillating Scores}
The hopeful goal was to find the set of variables that lead to not only a convergence,
but an almost "tug-of-war" battle when one model trains against the other and vice versa.
This is graphically shown via an oscillating crew score around the 
eventual convergence crew score. This would mean that the two models
are successfunlly balanced and able to improve their strategy with training time against
the opposition.

In an attempt to find a training session mathcing this quality

% grid search results.
\subsection{Model Evolution}
% are the agents "improving" or just changing minorly to trick each other
\subsection{Interpreting Communcation Vectors}
Unfortunately, we could not 
\subsection{Future Directions}
This approach is just a start into understanding how neural networks
communicate with one another. Although assumptions can be made,
understanding the actual information being transferred between each model is
a dark area. Innovative techniques must be found to analyze this information flow 
in order to fully comprehend the strategy within the game.

@@

Finally, similar work in adversarial networks could potentially give rise to
more techniques utilizing them. Generative adversarial networks are at the forefront of adversarial techniques, but possibly
large multi-agent adervasarial communication networks could give heed to more good results.
{\small
\bibliographystyle{ieee_fullname}
\bibliography{egbib}
}
\appendix
\section{Reproducibility}
\section{Framework}
\end{document}
